Spin canonical divisors of log stacky curves

### 2015-07-01 stacky_write_up/spin_cring.tex
comments on abstract

>>>>

\todo{Peter ``the study of'' is used twice in the first sentence.  Can we find a way to replace one of them?}

\todo{Peter: I don't like the use of ``In particular, this work..."  Can we say something like ``This paper ..."}

\todo{Peter: I don't understand the purpose of the parenthetical ``(or effective).''  What is it trying to say?}

\todo{Peter: I don't like the use of the word ``strongly'' in the third sentence; these sort of adjectives are ambiguous and subjective, and don't add any real content to the statement}

\todo{Peter: Get rid of comment about fractional weight modular forms.  This does not appear anywhere except in further questions, and does not deserve a spot in the abstract.}
